---
title: "NO2 Dataset Analysis"
date: "2024-03-17"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



## About NO2 Data Set

The "no2" dataset likely contains data related to nitrogen dioxide (NO2) concentrations in Germany.

### R Packages

```{r, warning=FALSE,message=FALSE}
library(gstat)
library(tidyverse)
library(sf)
library(viridis)
library(patchwork)
library(stars)
library(ggplot2)
```

### Read Data

```{r}
no2 <- read_csv(system.file("external/no2.csv", 
                            package = "gstat"), show_col_types = FALSE)
```

```{r,message=FALSE}
head(no2)
```

```{r}
dim(no2)
```

```{r}
colnames(no2)
```

```{r,message=FALSE}
summary(no2)
```

```{r,message=FALSE}
head(data.frame(no2), 3)

```

### Create a Coordinate Reference System (CRS) Object

```{r}
crs <- st_crs("EPSG:32632")
```

```{r,message=FALSE}
no2.sf <- st_as_sf(no2, crs = "OGC:CRS84", coords = 
                     c("station_longitude_deg", "station_latitude_deg")) |>
st_transform(crs) 
head(no2.sf)

```

### Spatial Visualization

#### Load country bondries

```{r,message=FALSE}
map <- read_sf("de_nuts1.gpkg") |> st_transform(crs) 
head(map)
```

```{r}
plot1 <-ggplot() + geom_sf(data = map) +  labs(title = "Country Map")
plot1
```

Figure 1 : Country map of Germany

```{r}
plot2<-ggplot() + geom_sf(data = map) + 
       geom_sf(data = no2.sf, mapping = aes(col = NO2)) + 
        scale_color_viridis() + labs(title = "NO2 concentration")
plot2
```

Figure 2 : Concentration of NO2

\- Figure 1 illustrates the spatial variability of NO2 concentrations, highlighting areas of concern and potential health risks associated with air quality.

```{r}
plot1 | plot2
```

Figure 3 : Combine map of country map and NO2 concentration

#### The inverse distance weighted interpolation

```{r,message=FALSE}
grid <- st_bbox(map) |>
  st_as_stars(dx = 10000) |> st_crop(map) 
grid


grid <- st_bbox(map) |>
  st_as_stars(dx = 10000) |> st_crop(map) 
grid
```

```{r}
st_crs(grid) <- st_crs(no2.sf)
```

```{r,message=FALSE}
interpolated.values <- idw(NO2~1, no2.sf, grid)
```

```{r,message=FALSE}
interpolated.values
```

```{r}
plot3<- ggplot() + geom_stars(data = interpolated.values, 
                      aes(fill = var1.pred, x = x, y = y)) + 
  geom_sf(data = st_cast(map, "MULTILINESTRING")) + 
  geom_sf(data = no2.sf, col="red") + scale_fill_viridis() +
  labs(title = "NO2 IDW interpolations")
plot3
```

Figure 4: Visualization of NO2 Concentration Interpolations Using IDW Method

-Figure4 represents **NO2 concentrations** across different regions on a map, likely corresponding to Germany given the shape and coordinates.

```{r}
plot2|plot3
```

Figure 5: Combine map of NO2 concentration and NO2 IDW interpolation

-The Figure 5 depicts the spatial distribution of **NO2 concentrations**, with red dots indicating observed values. The right side uses **IDW interpolations** to predict NO2 levels across the entire region.

### Variogram Cloud

```{r}
vcloud <- variogram(NO2~1, no2.sf, cloud=TRUE)
```

```{r}
plot4<- ggplot(data=vcloud, aes(x=dist, y=gamma)) + geom_point()+
    labs(title = "variogram cloud")

plot4
```

Figure 6: Cloud graph

-The Figure6 (**variogram cloud graph)** represents the spatial relationship between data points in a dataset.

```{r}
plot(vcloud)
```

Figure 7: Variogram cloud

#### Binned Empirical Semi-Variogram

```{r}
v1 <- variogram(NO2~1, no2.sf)
head(v1)
```

```{r}
plot(v1, plot.numbers = TRUE, xlab = "distance h [m]",
     ylab = expression(gamma(h)),
     xlim = c(0, 1.055 * max(v1$dist)), main="Sample Experimental Variogram")
```

Figure 8: Sample Experimental Variogram

#### Change default values

```{r}
v2 <- variogram(NO2~1, no2.sf, cutoff = 100000, width = 10000)
head(v2)
```

```{r}
plot(v2, plot.numbers = TRUE, xlab = "distance h [m]",
     ylab = expression(gamma(h)),
     xlim = c(0, 1.055 * max(v2$dist)))
```

Figure 9 : Sample variogram plot with adjusted cutoff and lag width

### Fitting the variogram model

```{r}
v.m1 <- fit.variogram(v1, vgm(psill=20, model = "Exp", range = 20000, nugget = 1))
plot(v1, v.m1, main="Exponential variogram model")
```

Figure10 : Exponential variogram model

-The Figure 9 (**variogram cloud graph)** represents the spatial relationship between data points in a dataset.

```{r,warning=FALSE,message=FALSE}
v.m2 <- fit.variogram(v1, vgm(psill=20, model = "Sph", range = 20000, nugget = 1))
plot(v1, v.m1, main="Spherical variogram model")
```

Figure 11 : Spherical variogram model

### Assess isotropy assumption

```{r,message=FALSE}
v1.ani <- variogram(NO2~1, alpha = c(0, 45, 90, 135), no2.sf)
head(v1.ani)
```

```{r}
plot(v1.ani, v.m1,main="Isotopy ")
```

Figure 12: Isotropy graph

-Figure 12 shows relationship with direction and NO2 concentration

#### Addressing anisotropy parameters

```{r}
v1.ani <- variogram(NO2~1, alpha = c(0, 45, 90, 135), no2.sf)
fit.ani <- vgm(psill=20, model = "Exp", range = 25000, nugget = 3, anis = c(30, 10, 0, 0.5, 0.3))
plot(v1.ani, fit.ani)
```

Figure 13: Addressing anisotropy parameters

## Variogram Map

```{r}
plot(variogram(NO2 ~ 1, no2.sf, map = TRUE, cutoff = 1000000, width = 10000))

```

Figure 13: Variogram map

-Figure 13 shows relationship with direction and NO2 concentration

### Kriging

#### Ordinary Kriging

```{r,message=FALSE}
krigOK <- krige(NO2~1, no2.sf, grid, v.m1)
krigOK
```

```{r}
plot6<-ggplot() + geom_stars(data = krigOK, aes(fill = var1.pred, x = x, y = y)) + 
  xlab(NULL) + ylab(NULL) +
  geom_sf(data = st_cast(map, "MULTILINESTRING")) + 
  geom_sf(data = no2.sf) +
  coord_sf(lims_method = "geometry_bbox") + scale_fill_viridis()+labs(title = "Oridinar Kriging of NO2")
plot(plot6 )
```

Figure 16: Visualization of NO2 Concentration Interpolations Using Ordinary kriging Method

-Figure 16 presents **NO2 concentrations** across different regions on a map, likely corresponding to Germany given the shape and coordinates.

```{r}
plot2|plot6
```

Figure 17: Combine map of NO2 concentration and NO2 Ordinary Kriging interpolation

## Cross validation

#### Ordinary kriging

```{r,message=FALSE}
krig.ok.cv <- krige.cv(NO2~1, no2.sf, v.m1, nfold=5)
krig.ok.cv[0:5,] 
```

#### IDW

```{r,message=FALSE}
idw.cv <- krige.cv(NO2~ 1, no2.sf, nmax = 7, nfold=5)
idw.cv[0:5,]
```

### Residual Mean Squared Error (RMSE)

```{r}
sqrt(sum(idw.cv$residual^2)/length(idw.cv$residual))
```

```{r}
round(sqrt(mean(krig.ok.cv$residual^2)), 2)
```

## Conclution

-   The variogram map highlights the spatial variability of NO2 concentrations, emphasizing areas of concern and potential health risks related to air quality.

-   The most suitable kriging method is ordinary kriging because there is no discernible trend, and the trent is an unknown constant.

-   In Figure 13, upon examining the variogram map, the presence of **isotropy** in the spatial distribution of the variable under consideration is evident.

-   There is no any spatial dependance.
